Marlowe: implementing and analysing financial contracts on blockchain

### 2020-02-25 papers/marlowe2019/paper.tex
line break
Add note about ongoing work on static analysis

\noindent
Here we expect Alice to deposit 850 Ada (850,000,000 Lovelace) into her \texttt{aliceAccount} before slot 100.
Otherwise, we \texttt{Close} the contract.

@@

>>>>

\noindent
Here we expect Alice to deposit 850 Ada (850,000,000 Lovelace) into her account \texttt{aliceAccount} before slot 100.
Otherwise, we \texttt{Close} the contract.

@@

\subsection{Future work}

At the time of writing, we are actively trying new optimisations and approaches for implementing static analysis that are more efficient in practise than the approach described in this paper. As a consequence, in some cases, the static analysis implementation can deviate considerably from the Haskell semantics. Our intention is to keep using property-based testing and formal verification to ensure that both implementations are consistent.
